Detecting Stylistic Variation in Pop Production

### 2023-11-29 outputs/paper/paper.qmd
table of content

The remainder of this paper is structured as:

@@

# Model

@@

# Results

@@

# Discussion

>>>>

The remainder of this paper is structured as: @sec-data details the data curation and extraction processes, including documentation on features from Spotify's audio features data set. @sec-model specifies the models used and @sec-results details their performance and most important predictors. @sec-discussion situates the study in the broader context of computational stylistics and recommendation systems, detailing how we can conceptualize "style" given the results and limitations of our study. We provide background on the Spotify features' provenance based on an interview we conducted with Glen McDonald, a principal engineer at Spotify.

@@

# Model {#sec-model}

@@

# Results {#sec-results}

@@

# Discussion {#sec-discussion}
